XXXXX

### 2014-09-28 paper/paper1.tex
RDF Validation Requirements Not Covered by OWL 2 QL

>>>>

\begin{table}
\caption{RDF Validation Requirements Not Covered by OWL 2 QL But by OWL 2 DL}
\label{tab:RequirementsCoveredOWL2DL}
\centering
\begin{tabular}{ll}
\hr
Requirements Classification & Requirements \\
\hr

\hr
\end{tabular}
\end{table}

\begin{table}
\caption{RDF Validation Requirements Not Covered by OWL 2 QL But by SPIN}
\label{tab:RequirementsCoveredSPIN}
\centering
\begin{tabular}{ll}
\hr
Requirements Classification & Requirements \\
\hr

\hr
\end{tabular}
\end{table}

\begin{table}
\caption{RDF Validation Requirements Not Covered by OWL 2 QL But by ShEx}
\label{tab:RequirementsCoveredShEx}
\centering
\begin{tabular}{ll}
\hr
Requirements Classification & Requirements \\
\hr

\hr
\end{tabular}
\end{table}

\subsubsection{RDF Validation Requirements Not Covered by OWL 2 QL But by OWL 2 DL}

\begin{itemize}
	\item OWL 2 DL as an instantiation of constraint languages which are high-level, human-friendly, and very expressive 
\end{itemize}

Table~\ref{tab:RequirementsCoveredOWL2DL}

\subsubsection{RDF Validation Requirements Not Covered by OWL 2 QL But by SPIN}

\begin{itemize}
	\item SPIN as an instantiation of constraint languages which are low-level and the most expressive 
\end{itemize}

Table~\ref{tab:RequirementsCoveredSPIN}

\subsubsection{RDF Validation Requirements Not Covered by OWL 2 QL But by ShEx}

\begin{itemize}
	\item ShEx as an instantiation of constraint languages which are high-level, human-friendly, intuitive, concise, and less expressive 
\end{itemize}

Table~\ref{tab:RequirementsCoveredShEx}
